Sequential rank agreement methods for comparison of ranked lists

### 2016-05-25 latex/superranker-manuscript.tex
minor adjustments

For an integer $1\le d\le P$ we define the expected set of unique
items found by merging the first $d$ elements across the possible
lists:
\begin{align}
S(d) &= \left\{X_p; \left(\sum_{r=1}^{P!} 1\left(r(X_p)\le d\right) Q(r)\right) >0\right\}\label{eq:sumset}\\
     &= \left\{X_p; Q(R(X_p) \leq d) > 0 \right\}\nn
\end{align}
where $1(\cdot)$ denotes the indicator function.
The empirical counterpart the set of unique items ranked less than or
equal to $d$ in any of the $L$ lists:
\begin{equation}
\widehat{S}_{L}(d) = \left\{X_p; \left(\frac{1}{L}\sum_{l=1}^L 1\left(R_l(X_p)\le d\right)\right)>0\right\},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.
We then define the \emph{sequential rank agreement} as the weighted
expected agreement of the items found in the set $S(d)$:
\begin{align}
  \textrm{sra}(d) = \frac{1}{|S(d)|}\sum_{p \in S(d)}A(X_p)\label{def:sra}
\end{align}
where $|S(d)|$ is the cardinality of the set $S(d)$.
The empirical counterpart is equivalently given by
\begin{equation}
  \widehat{\textrm{sra}}_L(d) = \frac{\sum_{\{p \in \widehat{S}_{L}(d)\}}(L-1)\widehat{A}_L(X_p)}{(L-1)|\widehat {S}_{L}(d)|}\label{def:sraEst}
\end{equation}

@@

The sequential rank agreement given in equation
(\ref{def:sra}) may therefore be rewritten as the following integral
with respect to $N$
\begin{align}
  \textrm{sra}(d) = \int_{1}^P \frac{A(X_p)}{N(P; d)}\mathrm dN(p; d).
\end{align}
The empirical sequential rank agreement is similarly given by
\begin{align}
  \widehat{\textrm{sra}}_L(d) &= \int_1^P \frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)}\mathrm d \widehat{N}_L(p; d) 
\end{align}
and it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\left|\widehat{\textrm{sra}}_L(d) - \textrm{sra}(d)\right| \leq \sup_{d \in 1,\ldots,P}\left|U_L(d)\right| - \sup_{d \in 1,\ldots,P}\left|V_L(d)\right|
\end{align}
where
\begin{align}
  U_L(d) &= \int_1^P\frac{A(X_p)}{N(P;d)} \mathrm d\left(\widehat{N}_L(p; d) - N(p; d)\right)\\
  V_L(d) &=  \int_1^P \left(\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right)\mathrm d\widehat{N}_L(p; d)
\end{align}
The conclusion of the proof therefore follows if each of these two
terms are uniformly of order $o_P(1)$ in $d$.  For the first term we
have that
\begin{align}
  \left|U_L(d)\right| \leq \left(\sup_{p \in 1,\ldots,P}\left|\frac{A(X_p)}{N(P;d)}\right|\right)\left(\widehat{N}_L(p; d) - N(p; d)\right)\biggr\rvert_1^P
\end{align}
where the second factor is $o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}). The first factor is $O(1)$ since $N(P;d)>0$
uniformly in $d$ and because $A(X_p)\le 2P^2$ u uniformly in $p$ \mcomment{double check bound}. It
thus follows that $\left|U_L(d)\right| = o_P(1)$ uniformly in $d$.

>>>>

For an integer $1\le d\le P$ we define the expected set of unique
items found by merging the first $d$ elements across the possible
lists:
\begin{align}
S(d) &= \left\{X_p; \left(\sum_{r=1}^{P!} 1\left(r(X_p)\le d\right) Q(r)\right) >0\right\}\label{eq:sumset}
\end{align}
where $1(\cdot)$ denotes the indicator function.
The empirical counterpart is the set of unique items ranked less than or
equal to $d$ in any of the $L$ lists:
\begin{equation}
\widehat{S}_{L}(d) = \left\{X_p; \left(\frac{1}{L}\sum_{l=1}^L 1\left(R_l(X_p)\le d\right)\right)>0\right\},
\end{equation}
which is exemplified in Panel (c) of Table \ref{tab:example}.
We then define the \emph{sequential rank agreement} as the weighted
expected agreement of the items found in the set $S(d)$:
\begin{align}
  \textrm{sra}(d) = \frac{1}{|S(d)|}\sum_{p \in S(d)}A(X_p)\label{def:sra}
\end{align}
where $|S(d)|$ is the cardinality of the set $S(d)$.
The empirical counterpart is equivalently given by
\begin{equation}
  \widehat{\textrm{sra}}_L(d) = \frac{\sum_{\{p \in \widehat{S}_{L}(d)\}}(L-1)\widehat{A}_L(X_p)}{(L-1)|\widehat {S}_{L}(d)|}\label{def:sraEst}
\end{equation}

@@

The sequential rank agreement given in equation
(\ref{def:sra}) may therefore be rewritten as the following integral
with respect to $N$
\begin{align}
  \textrm{sra}(d) = \int_{1}^P \frac{A(X_p)}{N(P; d)}\mathrm dN(p; d).
\end{align}
The empirical sequential rank agreement is similarly given by
\begin{align}
  \widehat{\textrm{sra}}_L(d) &= \int_1^P \frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)}\mathrm d \widehat{N}_L(p; d) 
\end{align}
and it follows that
\begin{align}
  \sup_{d \in 1,\ldots,P}\left|\widehat{\textrm{sra}}_L(d) - \textrm{sra}(d)\right| \leq \sup_{d \in 1,\ldots,P}\left|U_L(d)\right| - \sup_{d \in 1,\ldots,P}\left|V_L(d)\right|
\end{align}
where
\begin{align}
  U_L(d) &= \int_1^P\frac{A(X_p)}{N(P;d)} \mathrm d\left(\widehat{N}_L(p; d) - N(p; d)\right)\\
  V_L(d) &=  \int_1^P \left(\frac{\widehat{A}_L(X_p)}{\widehat{N}_L(P; d)} - \frac{A(X_p)}{N(P;d)}\right)\mathrm d\widehat{N}_L(p; d)
\end{align}
The conclusion of the proof therefore follows if each of these two
terms are uniformly of order $o_P(1)$ in $d$.  For the first term we
have that
\begin{align}
  \left|U_L(d)\right| \leq \left(\sup_{p \in 1,\ldots,P}\left|\frac{A(X_p)}{N(P;d)}\right|\right)\left(\widehat{N}_L(p; d) - N(p; d)\right)\biggr\rvert_1^P
\end{align}
where the second factor is $o_P(1)$ uniformly in $d$ by equation
(\ref{eq:countingConv}). The first factor is $O(1)$ since $N(P;d)>0$
uniformly in $d$ and because $A(X_p)\le 2P^2$ uniformly in $p$ \mcomment{double check bound}. It
thus follows that $\left|U_L(d)\right| = o_P(1)$ uniformly in $d$.
